Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-13 paper.qmd
Updated Figure 14

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2.5, 
               highd_data = scaled_mnist_data, 
               model_highd = scaled_mnist_data_model, 
               trimesh_data = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.92, 
                                 axis_pos_y = -0.92, 
                                 threshold = 0.06))

@@

mnist_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(0.5, 0.5), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-1.1, 0.9), 
  axis_text_size = 3.5, 
  is_category = TRUE) +
  interior_annotation(label = "b", cex = 2) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
    legend.position = "none"
  )

mnist_proj_tsne_model1_link <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1.1, 0.9), 
    axis_text_size = 4.5, 
    is_category = TRUE) +
  interior_annotation(label = "b", cex = 2.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  theme(
      legend.position = "none"
  )

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 2, 
               highd_data = scaled_mnist_data, 
               model_highd = scaled_mnist_data_model, 
               trimesh_data = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.83, 
                                 axis_pos_y = -0.83, 
                                 threshold = 0.06))

@@

mnist_proj_tsne_model2_link <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    axis_text_size = 4.5, 
    is_category = TRUE) +
  interior_annotation(label = "c", cex = 2.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  theme(
      legend.position = "none"
  )

>>>>

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2.5, 
               highd_data = scaled_mnist_data, 
               model_highd = scaled_mnist_data_model, 
               trimesh_data = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1.1, 
                                 axis_pos_x = -0.92, 
                                 axis_pos_y = -0.92, 
                                 threshold = 0.065))

@@

mnist_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(0.5, 0.5), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-1.1, 0.9), 
  axis_text_size = 4, 
  is_category = TRUE) +
  interior_annotation(label = "b", cex = 2) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
    legend.position = "none"
  )

mnist_proj_tsne_model1_link <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1.1, 0.9), 
    axis_text_size = 5, 
    is_category = TRUE) +
  interior_annotation(label = "b", cex = 2.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  theme(
      legend.position = "none"
  )

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 2, 
               highd_data = scaled_mnist_data, 
               model_highd = scaled_mnist_data_model, 
               trimesh_data = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1.1, 
                                 axis_pos_x = -0.83, 
                                 axis_pos_y = -0.83, 
                                 threshold = 0.065))

@@

mnist_proj_tsne_model2_link <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    axis_text_size = 5, 
    is_category = TRUE) +
  interior_annotation(label = "c", cex = 2.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  theme(
      legend.position = "none"
  )
